Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-21 revision-1/hyper.tex
checkpoint

\begin{definition}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ satisfies
  \emph{active confidentiality} iff
  it is malicious correct, and for all adversaries $\adversary$:
  %\begin{enumerate}
  %\item $\ \,\forall \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(\{ \outv \}|\store)) =
    %\support(\progtt(\prog,\adversary)(\{ \outv \}|\store))$
    %\item
    $$\begin{array}[t]{l}\forall \store_1, \store_2 \in \mems(S_H), \store \in \mems(\cinputs)\ . \\
    \quad
    \condd{\progtt(\prog,\adversary)}{O_H}{\store_1 \cup \store} =
    \condd{\progtt(\prog,\adversary)}{O_H}{\store_2 \cup \store} 
    %\qquad
    \implies
    %\quad
    \condd{\progtt(\prog,\adversary)}{\houtputs}{\store_1 \cup \store} =
    \condd{\progtt(\prog,\adversary)}{\houtputs}{\store_2 \cup \store}
    \end{array}$$
  %\end{enumerate}
\end{definition}

\begin{theorem}
  If $\prog$ satisfies active confidentiality for all $H,C$ then it is malicious secure.
\end{theorem}

\begin{definition}
  A protocol $\prog$ with has \emph{integrity} iff 
  $\forall \adversary . \runs_\adversary(\prog) \subseteq \runs(\prog)$.
\end{definition}

\begin{theorem}
  If a protocol has integrity it is malicious correct.
\end{theorem}

\begin{theorem}
  If a protocol is passive secure with integrity, then it satisfies active confidentiality.
\end{theorem}

\begin{theorem}
  If a protocol is passive secure with integrity, then it is malicious secure.
\end{theorem}

>>>>

\begin{definition}[Integrity]
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$ and $C$ 
  it is malicious correct and for all adversaries $\adversary_1,\adversary_2$
  and memories $\store \in \mems((S \cup O)_H)$:
    $$
    \condd{\progtt(\prog,\adversary_1)}{\houtputs}{\store} =
    \condd{\progtt(\prog,\adversary_2)}{\houtputs}{\store}
    $$
\end{definition}

\begin{lemma}
  \label{lemma-integrity}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  integrity, then for all adversaries $\adversary$
  and memories $\store \in \mems((S \cup O)_H)$:
  $$
  \condd{\progtt(\prog,\adversary)}{\houtputs}{\store} =
  \condd{\progtt(\prog)}{\houtputs}{\store}
  $$
\end{lemma}

\begin{theorem}
  If a protocol satisfies noninterference modulo output with
  integrity, then it is malicious secure.
\end{theorem}

\begin{proof}
  Let $\prog$ be some protocol with passive security and integrity
  where $\iov(\prog) = S \cup V \cup O$, and let $\adversary$ be some
  adversary.  Given some $\store\in S_H$, by definition of malicious
  correctness the simulator can extract inputs $\store' \in (S_C)$
  from $\adversary$ where $\idealf(\store \cup \store')$ is equivalent
  to the real world outputs. These can then be used in a simulated run
  of $\prog$ along with $\store \in S_H$ to generate a distribution
  of corrupt views of $\margd{\progtt(\prog)}{\houtputs}$.
  By assumption of integrity and Lemma \ref{lemma-integrity},
  this is the same as the real-world distribution of corrupt views
  in the presence of $\adversary$. 
\end{proof}

\begin{definition}
  An adversary $\adversary$ is \emph{passive} if it runs $\prog$ honestly,
  except for possible substitution of corrupt input secrets.
\end{definition}

\begin{lemma}
  Protocols with only passive adversaries have integrity.
\end{lemma}
